Pre working group data exploration: Mainly wrt coral cover

### 2024-07-29 julianna_data_exploration.Rmd
CV

>>>>

# CV: Noam's way

First try looking at CV Noam's way. I think this is more looking at if diverse areas (all time) are more stable, rather than if stability from one year to the next is dictated by current diversity (I think we can do this also since quadrats are fixed--will try that next)

## Calculate

Make a coefficient of variation function:

```{r cv function}
# coefficient of variation
CV <- function(x){
  return(sd(x,na.rm=T)/mean(x,na.rm=T))
}
```

Apply it when we summarize

```{r mega quadrat df}
# get mega df with just about anything we need
coralAlgDiv %>% 
  full_join(algSum) -> megaQuadDF
```

```{r calculate CVs}
diversity_stability <- megaQuadDF %>%
  dplyr::group_by(site, habitat, site_habitat, island_side) %>%
  dplyr::summarise(
    Coral_mean = mean(coral),
    Richness_mean = mean(Richness), 
    Richness_se = sd(Richness)/sqrt(n()),
    Richness_cv = CV(Richness),
    Shannon_mean = mean(Shannon), 
    Shannon_se = sd(Shannon)/sqrt(n()),
    Shannon_cv = CV(Shannon),
    Cover_mean = mean(AlgSum),
    Cover_se = sd(AlgSum)/sqrt(n()),
    Cover_cv = CV(AlgSum))
```

Algae diversity vs. cover CV:

```{r Shannon}
# divided by habitat
diversity_stability %>% 
  ggplot(aes(x = Shannon_mean, y = Cover_cv, color = site)) +
  geom_point() +
  facet_wrap(~habitat) +
  theme_bw()

# or all together
diversity_stability %>% 
  ggplot(aes(x = Shannon_mean, y = Cover_cv, color = site, shape = habitat)) +
  geom_point(size = 2) +
  theme_bw()
```

```{r richness}
# divided by habitat
diversity_stability %>% 
  ggplot(aes(x = Richness_mean, y = Cover_cv, color = site)) +
  geom_point() +
  facet_wrap(~habitat) +
  theme_bw()

# or all together
diversity_stability %>% 
  ggplot(aes(x = Richness_mean, y = Cover_cv, color = site, shape = habitat)) +
  geom_point(size = 2) +
  theme_bw()
```

Versus coral cover

```{r vs coral cover}
diversity_stability %>% 
  ggplot(aes(x = Coral_mean, y = Cover_cv, color = site, shape = habitat)) +
  geom_point(size = 2) +
  theme_bw()
```

# Stability

Is change in algal cover in a given quadrat from one year to the next influenced by diversity? Need to set up a lag/change to calculate this

# Synchrony

Maybe try this way: https://cran.r-project.org/web/packages/codyn/vignettes/Community_Stability_Metrics.html using the `codyn` package?

```{r}
